Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2021-01-19 journal paper/content/related_work.tex
trim some refs

%A long line of work from electrical engineering and computer science, starting from
%\citet{MultiPlayerMAB-Poor08,MultiPlayerMAB-Liu10,MultiPlayerMAB-Anima11}, focuses on competition for resources, not competition for consumers. Specifically, this literature targets an application to \emph{cognitive radios}, where multiple radios transmit simultaneously in a shared medium and compete for bandwidth. Each radio chooses channels over time using a multi-armed bandit algorithm. This work studies a repeated game between bandit algorithms, and focuses on designing algorithms which work well in this game, under various assumptions on communication, synchronization and collisions.

>>>>

A long line of work from electrical engineering and computer science, starting from
\citet{MultiPlayerMAB-Poor08,MultiPlayerMAB-Liu10}, focuses on competition for resources, not competition for consumers. Specifically, this literature targets an application to \emph{cognitive radios}, where multiple radios transmit simultaneously in a shared medium and compete for bandwidth. Each radio chooses channels over time using a multi-armed bandit algorithm. This work studies a repeated game between bandit algorithms, and focuses on designing algorithms which work well in this game, under various assumptions on communication, synchronization and collisions.
